Jesse Lu

### 2012-06-14 resume/bina/cover_letter.tex
Cover letters and resumes for 4 job applications done.

\begin{document}
% \maketitle
\thispagestyle{empty}
\part*{\center Jesse Lu}
\section*{Who am I? A problem solver.}
Not every problem, not all problems, and not by myself;
    but at the heart of it, solving problems is what I do well,
    it's what I enjoy doing, and it's what I would like to do at
    COMPANY.

I want to join COMPANY in solving technically-challenging, world-changing problems.

@@

In conclusion, I believe that great companies are simply a collection of great problem-solvers
    tackling great problems and I hope to join COMPANY in doing 
    so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.
\end{document}

>>>>

\begin{document}
% \maketitle
\thispagestyle{empty}
\part*{\center Jesse Lu}
\section*{Who am I? A problem solver.}
Not every problem, not all problems, and not by myself;
    but at the heart of it, solving problems is what I do well,
    it's what I enjoy doing, and it's what I would like to do at
    Bina.

I want to join Bina in solving technically-challenging, world-changing problems.

@@

In conclusion, I believe that great companies are simply a collection of great problem-solvers
    tackling great problems and I hope to join Bina in doing 
    so\footnote{\texttt{jesselu@stanford.edu, (408)568-9356, East Palo Alto, CA.}}.
\end{document}
